Are we living in a depressive society?

### 2024-04-19 outputs/paper/paper.qmd
update the format

* Is there codependency of social connection on one's depression level?

Through this analysis, we aim to better understand contributing factors of mental wellness of the US population. Furthermore, we display possible correlation between factors and the mentall wellness states.

@@

@@

```
@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:

@@

## Future Research
For future research, survey can further ask what are the factors that affect their mood.

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

>>>>

Through this analysis, we aim to better understand contributing factors of mental wellness of the US population. Furthermore, we display possible correlation between factors and the mental wellness states.

@@

@fig-sexandtrend-graph differentiates between the two sex subgroups, highlighting the trends in depressive disorder rates for each:

@@

@@

## Future Research
Given the self-reported nature of the data, researchers should be cautious about biases inherent in self-report surveys, such as social desirability bias or recall bias. Additionally, because the dataset represents a specific period (COVID-19 pandemic), care should be taken when generalizing findings to other times or situations. Mitigating these risks involves robust statistical techniques, clear reporting of the survey's scope and limitations, and, where possible, validation with other data sources. Furthermore, beyond studying the impact of COVID-19, the dataset could be used for longitudinal studies on public health trends, economic analysis, and social science research. It can serve as a baseline for future crises management studies, or for comparative studies on how different demographics cope with societal stressors.
